% !TEX root = GovChain.tex

In this section we describe a basic infrastructure for publishing government data that allows anyone with a single data entry to challenge the veracity of the data in case it was manipulated. We also provide a simple protocol that enables us to increase the trust of the general public in the data provided by the government. We achieve both of these objective without modifying the way that the government currently publishes or stores their data. We start by recapping basic cryptographic primitives we will be using in the remainder of this paper.

\medskip
\noindent{\bf Cryptographic primitives.} The first cryptographic primitive we will be using is that of {\em cryptographic (digital) signature}. Roughly, one can view the digital signature protocol as consisting of the following three components: \francisco{I would rather use ``cryptographic signatures''}
\begin{itemize}
\item A pair $(\sk,\pk)$, where $\sk$ is the secret key known only to a user, and used to generate signatures, and $\pk$ is the public key is given to everyone in order to verify that a message's signature was indeed signed by the owner of the secret key $\sk$.
\item The method $\sign(\sk,\m)$, allowing a secret-key holder to sign the document data. 
\item The method $\verify(\pk,\m,\mathit{sig})$ that allows anyone to verify if $\mathit{sig}$ is a valid signature of the document $\m$ by the entity corresponding to the public key $\pk$.
\end{itemize}
The signature protocol is required to be sound. This means that it verifies correctly, in a sense that $\verify(\pk,m,\sign(\sk,m))$ is always true, and that signatures are unforgeable without the secret key $\sk$. There are many digital signature schemes currently in use, for more details we refer the reader to \cite{KatzLindell2014}. We also point out that a large number of governments have adopted digital signatures as standard, mandatory procedures.

The second primitive we recall is that of {\em cryptographic hash functions}. Roughly speaking, a cryptographic hash function is any function $h$ that takes as input an arbitrary sized document, and produces a fixed size output, can be efficiently computable, and satisfies the following two properties:
\begin{itemize}
\item {\em Hiding.} This means that for any given input $x$, it is infeasible to compute $x$ if the only information we have is the value $h(x)$.\footnote{Strictly speaking, this also includes a random number $r$ coming from a distribution with high min-entropy, and being given $h(r||x)$ instead of $h(x)$.}
\item {\em Collision resistance.} Meaning, that it is infeasible to efficiently find two different values $x$ and $y$, such that $h(x)=h(y)$.\francisco{Should we state first and second collision properties for the sake of completeness?}
\end{itemize}
Notice that the hiding property allows us to use $h(x)$ as an encrypted digest of our document $x$, since we can not reconstruct $x$ from $h(x)$ alone, and the value $h(x)$ is of fixed size, even for documents $x$ whose size is in TBs. On the other hand, collision resistance ensures that in order to prove to someone who has only $h(x)$ that we have $x$, we need to provide said $x$. To the date of this writing, there are a number of cryptographic hash functions in use. Most protocols adopt the NIST Secure Hash Algorithms\cite{sha_standard}, which include SHA-256 and SHA-512 from the SHA-2 family, but other hash functions are considered equally secure and even more efficient. We highlight the BLAKE2 algorithm, released after the SHA-3 competition, which is more secure and faster than SHA-1 and SHA-2. For a more detailed treatment of cryptographic hash functions we refer the reader to \cite{sha_standard,aumasson,sha3zoo,bitcoinbook}. \francisco{Took the liberty of changing this paragraph (from ``To the day...'' on) and adding some references. Feel free to come back to previous versions}

\medskip
\noindent{\bf Hash lists and Merkle trees.}
\francisco{Feel free to change the following, I'm not very inspired.} 
In this section, let $h$ be a fixed cryptographic hash function. A hash list is an ordered list of data $d_1,d_2,\dots d_k$ such that every element of the list contains the hash value of the previous element, \ie $h(d_1)\in d_2$. In a hash list, modifying an element affects the value of all succesive elements, and because of the collision resistance of $h$, it is unfeasible to replace an element of the list without having to replace all succesive elements. Therefore, if the last value of the list is permanently monitored, there is virtually no way of modifying an element of the list while keeping the structure of hash list and not being detected. This is one of the core ideas behind Bitcoin's protocol \cite{whitepaper}, but it has been used widely in a number of precedent applications. For instance, \francisco{incluir ejemplo del Pinpass aquí...}

In contrast to a hash list, a Merkle tree is \francisco{...}

\medskip
\noindent{\bf Basic steps to gain trust.} Now that we understand the basic data structures that can guarantee immutability of the data, we can show how they can be used to provide compact certificates that no data was manipulated. The basic idea is quite simple: the government will keep on publishing their data as they do at the present, but at regular intervals, they will also publish a compact cryptographic digest of the new data. Assume that $d_1,d_2,\ldots ,d_n$ is the list of the documents published during one working day. Furthermore, assume that the order in which this list was published is made available in the day's digest. At the end of the day, the government will also create a Merkle tree $MT(d_1,\ldots ,d_n)$, whose leaves are the hash values of these documents, that is, the values $h(d_1),\ldots ,h(d_n)$. At this point, the government publishes $MT(d_1,\ldots ,d_n)$, together with the cryptographic signature of this data corresponding to the public key under which the government agreed to publish their data. The fact that the signature matches the data in the Merkle tree and the government's public key, allows us to easily verify that the data is legitimate, assuming that the government will keep their secret keys safe.

As explained above, anyone who downloads the root of this Merkle tree (representing typically less than 100 bytes of information), can check whether the data corresponding to that single day was modified by downloading it in the sequence provided by the government, hashing it, and assembling a Merkle tree starting from these hashes. If the Merkle root published by the government does not match the one computed using this method, the verifier can know for certain that the data had been manipulated. It is reasonable to assume that the government also makes it public knowledge which hashing algorithm and Merkle tree assembly they will be using, according to Kerckhoff's principle.

Notice that if we want to be able to detect which particular documents were modified, we would have to store the entire Merkle tree. The size of this will be in tens of megabytes for a tree coding one million documents when using SHA-256 as the hash function, so one might argue that even this is a reasonable amount of storage needed to pinpoint which particular data had been manipulated. One can further restrict the amount of needed storage by storing fewer layers of the Merkle tree (i.e if one trims the original leaves the size will roughly half), but also losing the granularity at which manipulations can be detected. For instance, if we store the tree up to the next to last level, we can check if one of the two adjacent documents in the list $d_1,\ldots ,d_n$ have been modified, but will not be able to say which one (Figure \ref{fig-trim}). Based on the volume of the published data, the government might also wish to publish these partial trees and sign them, in order to make it easier for a person to store this information.

We can actually do better by utilizing the same idea that Bitcoin uses to store its blocks \cite{whitepaper}, and encode and/or publish the hash of the previous day's data in the current day's digest. That is, we can create a hash list of the Merkle trees roots published each day. This would mean that storing one day's Merkle tree would not only assure that the data of that particular day can not be manipulated, but also, it would assure that the data in any of the days previous to this one could not be manipulated.  That is, since each tree would also contain the hash value of the previous day's digest, we can simply follow this chain day after day, and see if any of the hash values do not match. This simple concept is illustrated in Figure \ref{fig-merkle-chain}.


\medskip
\noindent{\bf Increasing credibility.} Of course, the solution we just proposed suffers from a similar issue as just publishing government data without the additional list of hashes and Merkle trees. Namely, if no one guards the hash list, or the Merkle tree, the government is free to change the data, recompute the new Merkle trees and hash lists, and publish them as if they were the original ones. Similarly, if someone does possess a single document they wish to show was changed, even if they have the Merkle tree for that day, it would still be a dispute between the government (claiming that the data that is presently published is the correct one) and this person, so it could be difficult to decide whose claim is the actual truth.

A rather simple solution to this problem is to involve non-profit organizations that wish to monitor the state of democracy into this process. More precisely, such organizations would guard some degree of the meta information published by the government, and periodically download the government's documents for some particular day, compute their hash values, and check that the Merkle tree obtained in this way matches the one published by the government. In particular, once that the government publicly announces its schema for publishing the data and additional security certificates (Merkle trees and hash lists) it would be simple to build an automated tool that helps organizations that wish to verify government's data to do so. Depending the organization's capacity, the tool could provide various levels of storage and verification requirements. In particular, the tool would support:
\begin{itemize}
\item Storing only the Merkle tree's root, together with the hash of previous day's data. This is a very lightweight solution that can be supported even on mobile devices, as it requires storing one or two hash values per day (depending on the implementation). Using this value, a day's data can be verified for modifications at a later date by downloading and hashing it.
\item Storing the entire Merkle tree, plus the hash of previous day's data. As explained above, this allows detecting modifications and tracing which particular documents suffered changes.
\item A hybrid solution storing the Merkle tree up to some level, allowing less granularity than storing the entire tree.
\item In terms of verification, the tool would provide support to verify the data of a particular day by downloading it, hashing it, and check that the resulting Merkle tree is correct. Additionally, the tool could verify backwards compatibility by also following the hashes of previous day's data, and checking that they match (for a certain period or the entire history).
\end{itemize}

Note that in terms of storage, none of these solutions would be very expensive, and can in a sense serve as guarantors of the published data on government's pages. Additionally, if the amount of these organizations is sufficiently large, and in particular if they are dispersed around the globe or untraceable, it becomes very unlikely that a malignant agent would be capable of subverting all of their data. Furthermore, the fact that the lightest level of this solution could even be stored on mobile phones, makes it feasible for interested individuals to guard the security certificates and check their veracity later, or effectively detect malicious guarantors.