The philosophy behind the Open Government Data initiative is based on the idea that making the government data freely available to the general public will make the democratic process more transparent, and the government institutions accountable for their actions. There is already a large number of governments that have committed to opening up their data, for instance \url{data.gov} in the US, \url{data.gov.uk} in the UK, and \url{data.gov.in} in India, to name a few. International institutions such as The Organisation for Economic Co-operation and Development (OECD) are also openly promoting the adoption of the open data policy\footnote{\url{http://www.oecd.org/gov/digital-government/open-government-data.htm}}.

Despite the increasing enthusiasm around the initiative, there are also sceptic voices that illustrate some vulnerabilities of systems for publishing government data. For instance, a recent report by the Economist Intelligence Unit \cite{economist} found that there is a non negligible percentage of the population concerned by the governments' ability to keep the data secure from a modification by third parties. Similarly, there is a raising concern that the government might be manipulating historical data or erasing records \cite{poynter}.

In both of these examples, it might be difficult even for an investigative journalist with significant institutional support to prove foul play with regard to government records. First of all, they would have to keep a copy of the government data. Given the volume of the data that the government publishes, this can be prohibitively expensive. Second, even if a person had an (alleged) local copy of the data, how are we to know whether they modified this copy, or whether the government, or a third party did it with the data that is currently available? In any case, we would need to assign an arbiter to decide the dispute, which leads to similar trust issues.


%After all, to challenge the veracity of the data that is publicly available, one usually uses a local copy they made previously, showing it to be different to the actual data\footnote{In practice one might use a more elaborate mechanism that includes web records or cached web pages, but our point still remains valid.}. But how are we to know whether the challenger modified his the copy of the data, or whether the government, or a third party did it? In any case, we would have to assign an arbiter to decide the dispute, thus relying on one single institution (a judge or a tribunal most likely), which can lead to similar trust issues.


Fortunately, the technology behind cryptocurrencies (generally referred to as \emph{blockchain technology}) allows us to remove both of these issues on a technological level. The basic solution is quite simple, and does not even require a major disruption to the way that the government publishes data. This solution simply relies on the blockchain data structure underlying Bitcoin \cite{whitepaper,bitcoinbook}. In essence, a blockchain is a linked list where each element stores not only its data, but also a cryptographic hash of the previous element of the list \cite{bitcoinbook}. The government can then publish its data in this format, signing each element of the list (also called a block) with its private key in order to confirm the identity of the publisher.
%Note that this solution is basically identical to simple centralized cryptocurrencies such as Scroogecoin \cite{bitcoinbook}.

By the properties of cryptographic hash functions, the only piece of information we need to store in order to assure that the data has not been modified up to some specific element of the list is the hash value of that element. Because of this, storing the government data in a blockchain allows us to resolve the two issues discussed above. First, to make sure the data has not been tampered with, one does not need to store the data itself, but only store a hash value of the last block. Even if one stores this information frequently, it will still be small enough to be handled even by smartphones. Second, since storing the information required to assure that the data has not been manipulated is cheap, multiple copies can be made available from trusted sources (e.g. non profit organizations, public activists, concerned citizens, etc.), thus making it infeasible to manipulate all of these sources by a malicious agent.



%While the term blockchain is often used to describe Bitcoin's public ledger and various elements used in the decentralization protocol involved in deciding what data will be written on this ledger (see \cite{NarayananC17} for a good overview), here we will use the term blockchain to refer to simple hash-list that assures we can detect when the data in some previous block has been modified. We  therefore think of a blockchain as a list where each element stores not only its data, but also a cryptographic hash of the previous element of the list \cite{bitcoinbook}. By the properties of the hash function, the only piece of the information we need to store in order to assure that the data has not been modified up to some specific element of the list the hash value of that element. 



%Storing the government data on a blockchain allows us to resolve the two issues discussed above. First, in order to assure that the data has not been modified we do not need to keep a copy of the data itself, but only of its cryptographic hash \cite{bitcoinbook}, which can be done even on a modern phone, and does not require a prohibitive amount of storage. Second, since storing the information required to assure that the data has not been manipulated is so cheap, multiple copies can be made available from trusted sources (e.g. non profit organizations, public activists, etc.), thus making it infeasible to manipulate all of these sources by a malicious agent.

%While it is certainly feasible to develop a simple blockchain for publishing government data (basically implementing a Scroogecoin based solution described in \cite{bitcoinbook}), and achieve the guarantees sought in the scenarios we just described, this solution might run into some issues when managing government data. More precisely, we would like to tackle the following problems:

While this simple solution does work in resolving the two issues outlined above, due to the way that government data is managed and published, applying it ``out of the box" might not be feasible. Next, we list several technical challenges that need to be resolved in order to make it possible to publish government data in a blockchain:
\begin{itemize}
\item {\it Credibility.} The mistrust of the general public is not solved by simply publishing the data on a (centralized) blockchain. Most notably, if there is not enough interest by non-profit agencies or the general public to occasionally back up the latest hash (and possibly check the veracity of the information), the publisher can change the data, recompute the blockchain, and upload it again. Moreover, there is no way to verify whether the information has been modified, the dispute is simply a matter of trusting the evidence provided by the involved parties. %To resolve this, we therefore propose to occasionally publish hashes of the government's blocks on a well established decentralized blockchain such as e.g. Ethereum, and issue certificates to the current state of the governments' blockchain.
\item {\it Persistence.} By its nature, the records that the government keeps are often updated to fix typos or reflect new findings. On the other hand, the data on a blockchain is immutable once published. It is therefore important to design a blockchain-based platform for government data that allows updates to the information, and tracks them in an  immutable way.
%\item {\it Tracking documents.}
%Since the volume of data that the government publishes might be large, it can be difficult to locate a specific document that one has at hand. In particular, the document's hash will probably be ``hidden" in the Merkle tree for the particular block that the document is in, thus making it difficult to find.
%Given the relatively large number of documents published by governments and the fact that storing records in the blockchain is expensive, it is not reasonable to store a different identifier for each document in the blockchain. Instead, one could store enough information to allow for irrefutable timestamped proofs of existence for documents using less space in the blockchain (e.g. use a Merkle tree and only store its root in the blockchain). Unfortunately, this introduces the need to have additional information for tracking a document, as the document itself is not enough to produce an identifier that can be verified in the blockchain.
%\francisco{I find this Merkle tree occurrence too son.}\martin{I re-wrote this part considering that the issue is not the large amount of data but the fact that the documents' hashes cannot be verified without a certificate}
%Furthermore, it might be difficult to verify if this particular document was ever ``committed" to a public backup of the data described in point one above, since the document's hash will probably be ``hidden" in the Merkle tree for the particular block it is in.

\item {\it Clairvoyance attacks.} Note that using a blockchain-based solution the government can commit to never changing its secret and sensitive data by publishing their hashes. However, it might be possible for a misbehaving government agent to publish various versions of the same document in the blockchain, and in the case of a dispute reveal only the one suiting them best. Since the data itself is published through cryptographic hashes, it will be impossible to differentiate such versions unless an interested party has the content of two contradicting documents (plus a proof that their hashes are linked to the blockchain).
%\item {\it Infrastructure issues.} Finally, we have to address the way that government data is created and stored, and the way that particular hash functions can be made vulnerable is not used properly. 
\end{itemize}

In this paper we describe the components of a platform for publishing government data that aims at resolving the technical challenges outlined above. In particular, we resolve the credibility issue by publishing occasional hashes of the latest blocks of our blockchain on a public blockchain supporting smart contracts (in our case Ethereum). The objective of this is precisely to avoid trust issues regarding historical data: a dispute about a document can be settled with a simple proof that relies on the immutability of the Ethereum blockchain. The persistence issue is solved by designing a specific data structure to be stored on each block. Finally, the problem of clairvoyance attacks is solved by a practical requirement: documents stored in the (private) blockchain must be either made publicly available or, if only a \emph{commitment} to a document is published, then the main topic of the document must be described. Then, when settling a dispute a judge could ask to disclose certain documents (with a proof of correctness based on the commitment) based on this descriptions.

%\francisco{I am a bit skeptic about this phrase. I would rather say that clairvoyance attacks can be avoided, but at the expense of flexibility (you have to impose some format of the target documents, like json objects as in \cite{energiaabierta})}

We would like to note that this paper is certainly not the first one to consider blockhain-based technologies for managing government data. Indeed, this idea has been around for a while, and ranges from fully fledged public blockchains recording every action of the government \cite{eushit,ibmshit}, to smaller scale solutions that track a fixed series of data items \cite{energiaabierta}. What we believe makes our solution technically interesting is the idea of allowing the data to be updated and secured using smart contracts, while requiring very few interactions with a public blockchain (which makes the implementation surprisingly cheap). Another interesting feature of our contribution is that we present a different point of view: instead of empowering the public with complex tools to retrieve every possible document and its history, we follow the principle that any claim about the history of a document can be either proven true or false without room for interpretation. This allows us to have an very simple and secure protocol in which the government is completely accountable for its actions. Finally, we do not provide only a conceptual description of our solution, but also specify the components needed to make it work in junction with the Ethereum platform.

In the sequel we recall the basic properties of hash functions and public signatures. Then, we provide a simple protocol for publishing government data using a private blockchain that has the benefits mentioned above. Finally, we discuss the technicalities behind this protocol and how it can be linked to the Ethereum network via a simple smart contract.
